An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-08 poly-embed-journal/poly-embed-journal.tex
Meeting notes

\jessie{Lemma X}
\begin{lemma}
  Let $\risk L: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $\risk L(p) = \min_{v \in \V} \inprod{v}{p}$.
  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L$ and let $\Gamma := \prop{L}$.
  Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
  % Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
  \begin{enumerate}
  \item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
  % \item $\R^*$ is a minimum representative set for $L$,
  \item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
  \item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$.
  \end{enumerate}
\end{lemma}
\newcommand{\epi}{\mathrm{epi}}
\begin{proof}
  Since $\risk L$ is a concave polyhedral function, it is finitely generated by \citet[Corollary 19.1.2]{rockafellar1997convex}. %and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.  My copy of Rockafellar is in COS right now.}.
  By the \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
  Form $\V$ by iterating over $E_L$'s finitely many faces as follows:
  for each face $F$, we know there is a vector $v$ generating the face \jessiet{That is, $p \mapsto (p, \inprod{p}{v})$ supports $\risk L$ on [exactly] face $F$.}. 
  If there is a point $p_v \in F$ such that $\risk L$ is differentiable at $p_v$,\jessiet{Is this the condition we want? Dancing around facets} add $v$ to $\V$.

>>>>

\jessie{Lemma X}
\begin{lemma}
  Let $f: \reals^n_+ \to \reals_+$ be a (concave) polyhedral function.
  There exists a unique set of loss vectors $\V$ of minimum cardinality such that $f(p) = \min_{v \in \V} \inprod{v}{p}$.
  Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = \risk L(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V\}$.
  Furthermore, let $L: \R \to \reals^\Y_+$ be any loss with Bayes risk $\risk L := f$ and let $\Gamma := \prop{L}$.
  Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
  % Furthermore, for all losses $L: \R \to \reals^\Y_+$ with Bayes risk $\risk L : \reals^n_+ \to \reals_+$, letting $\Gamma := \prop{L}$, there exists an $\R^* \subseteq \R$ such that
  \begin{enumerate}
  \item $\{L(r^*) \mid r^* \in \R^*\} = \V$,
  % \item $\R^*$ is a minimum representative set for $L$,
  \item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
  \item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
  \end{enumerate}
\end{lemma}
\newcommand{\epi}{\mathrm{epi}}
\begin{proof}
  Since $\risk L$ is a concave polyhedral function, it is finitely generated by \citet[Corollary 19.1.2]{rockafellar1997convex}. %and therefore, the set of linear functions of minimum cardinality is well-defined and unique\jessiet{unique should be cite-able, but not sure where to find it.  My copy of Rockafellar is in COS right now.}.
  By \citet[Theorem 19.1]{rockafellar1997convex}, we know that $E_L := \epi(\risk L)$ is closed and has finitely many faces.
  \jessiet{Define convex function on positive orthant that is the negative one homogeneous version of negative risk. $G : \reals^\Y_+ \to \reals$ given by $G(v) = -\risk L(v/\|v\|_1)  \|v\|_1$ with $G(0) = 0$.  Talk about epigraph and subgraients of $G$.}
  Form $\V$ by iterating over $E_L$'s finitely many faces as follows:
  for each face $F$, we know there is a vector $v$ generating the face \jessiet{That is, $p \mapsto (p, \inprod{p}{v})$ supports $\risk L$ on [exactly] face $F$.}. 
  If there is a point $p_v \in F$ such that $\risk L$ is differentiable at $p_v$,\jessiet{Is this the condition we want? Dancing around facets} add $v$ to $\V$.
